---
title: "Bayesian linear regression"
author: "Bakhtawar Noor"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Blm Package

The Blm package is an R package for Bayesian Linear Regression. 


## Installation of the Blm Package
The process to install Blm package is as follows:
1. Install the package "devtools". You can skip this step if it's already installed and you can proceed.

```{r setup, include=FALSE}
install.packages("devtools")
```


2. Load the package "devtools" into R.

```{r setup, include=FALSE}
library(devtools)
```


3. Unfortunately, the Blm package is only available through github. Therefore, install the Blm package from github.

```{r setup, include=FALSE}
install_github("bioinfau/blm")
```


## Functions in the Blm Package

1. blm

This function returns a fitted model. However, for this function to work, the user needs to provide a formula the hyperparameters alpha and beta. 


2. confint

This function returns the confidence interval for the fitted parameter. The user needs to provide the fitted model obtained for the blm function and a confidence level (0.95).


3. coefficient

This function returns the fitted paramters of the model. The user needs to provide the fitted model.


4. predict

This function makes prediction based on the fitted model. The user needs to provide the fitted model and new data (optional). If new data is not provided, the function will make predictions based on the old data.


5. residuals
This function returns the residuals of the fit. That is the difference between predicted values and observed values for the response variable. The user needs to provide the fitted model.


6. Fitted

This function gives the fitted response variables. This is not the response variables in the data you fitted the model to, but instead the predictions that the model makes. The user needs to provide the fitted model.


7. deviance

This function just computes the sum of squared distances from the predicted response variables to the observed. The user needs to provide the fitted model.


8. plots

This function makes a simple plot(s) for the response variable and the predictor variable. The use needs to provide the fitted model.


9. print

This function prints how the fitting function was called and what the fitted coefficients are. The user need to provide the fitted model.


10. summary

This function prints how the fitting function was called, the fitted coefficients and the residuals of the fit. The user needs to provide the fitted model.